---
output: github_document
---

# UNICEF Package
This package will allow you to fetch datasets from the sdmx API of UNICEF.

## Install Package
In order to install UNICEF package, you have to first install devtools package

```{r eval = FALSE}
install.packages("devtools")
library(devtools)
```

```{r eval = TRUE, include=FALSE}
install.packages("devtools", repos ="http://cran.us.r-project.org")
library(devtools)
```

And then install our package and add to library

```{r eval = FALSE}
install_github("tunay5/UNICEF",force = TRUE)
library(UNICEF)
```

```{r eval = TRUE, include=FALSE}
install_github("tunay5/UNICEF",force = TRUE)
library(UNICEF)
```


## dataflows()
This code will return the dataflows included in UNICEF database. It also include other features of dataflows, such as its agency id, name and dataflow id.

```{r eval = FALSE}
dataflows()
```

```{r echo = FALSE, error = FALSE, message=FALSE}
data <- dataflows()

data[1:10,]
```


## get_data()
With the \code{get_data} function, you will be able to fetch data based on the dataflow and filter features, from the database of UNICEF.

For example, if you want to fetch the data of child mortality rate (under 5 years old) in São Paulo, from the years of 2010 and 2012:

```{r eval = FALSE}
get_data(dataflow = "BRAZIL_CO", filter = list(c("SP"),c("MORTALIDADEINFANCIAMENOR5"),c(NA), c(NA)), start = 2010, end = 2012)

```
As you can see, for \code{filter} variable you should create a list and add each object in the in the order that UNICEF represents in its website.

```{r eval = TRUE, include = FALSE}
data <- get_data(dataflow = "BRAZIL_CO", filter = list(c("SP"),c("MORTALIDADEINFANCIAMENOR5"),c(NA), c(NA)), start = 2010, end = 2012)
```
 
```{r echo = FALSE}
data
```

## Notes
To check the data queries, metadata and reach to the database, check:
<https://sdmx.data.unicef.org/overview.html>

To understand the sdmx API of UNICEF:
<https://data.unicef.org/sdmx-api-documentation/>

